HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-14 hermes_paper/hermes_paper.tex
remove we/our formulation

Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals. Our model is decomposed  into two parts: local predictors and a global corrector.  First, a per-time-series parametric statistical model is trained on all sequences. Then,  a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models. By adding external weak signals in our proposed framework, we show the real potential of the hybrid approach: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
%Our new hybrid framework is divided in two parts. As a first step, we compute a per-time-series forecast for each trend using any kind of parametric models. Then, gathering information of the first prediction and external variables, a global error corrector neural network is trained to correct weaknesses of the first forecast.

@@

The paper is organized as follow. Section~\ref{sec:hybrid} describes our hybrid framework. Then, we present our new fashion dataset in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes our results and comparisons with several benchmarks. Finally, we detail research perspectives and conclude our paper in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector. We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.

@@

During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor result and instability. In this paper, we provide a general framework able to deal with any kind of per-time-series models. In Section~\ref{sec:exp}, we present two versions of our framework. The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction. %The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.

In the specific application of fashion trends prediction, we detected and defined two main forms of standard weaknesses for a univariate parametric forecast as defined above. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that we mainly unknow the exact influence of external variables on the main signal. It is on this point that our new hybrid framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals. First forecast examples of our new hybrid model are given in Figure~\ref{fig:introexamples}

@@

The second part of our model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. First, we provide  to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors. Second, as we did not make any assumption about the scale of our time series, we have to carefully normalize them before feeding them to the RNN.
Consider the following pre-processing. 
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$, 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad\mbox{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
$$

@@

Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, see Table~\ref{tab:metricresults}. Then, to correct the second form of weakness, in addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$. For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$. Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals linked to the $n$-th sequence. In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence. Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for the RNN,   
$$
\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
$$
Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
%$$
%\tspred^n_{T+i|T} 
%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
%$$
\begin{equation}
\label{eq:withws:full:model}
\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
\end{equation}

@@

\subsection{Translate fashion to data}

A collection of vision neural networks have been designed and trained  at detecting clothes details on pictures: cloth type (pants, shoes, top etc...), form, size,color,texture etc... Then, with the knowledge of a team of fashion experts, these clothes details was aggregated in order to define a fashion trend: a meaningfully combination of items that represents an existing trend in the fashion sphere. To represent finely the society behaviours based on social media, a group of thousands of random users, called a panel, have been created on several geolocalisations. Analysing every day images shared on social networks by these panels with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.

\subsection{Fashion dataset}

@@

In addition to this paper, a fashion dataset is proposed. It contains an sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. A collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. Some sequences show interesting behaviours with sudden changes. We call them emerging or declining trends depending on the change in direction. A central point of this work is to accurately detect and forecast these trends.

@@

In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. In this way, we add to our large dataset several weak signals for each sequence.

Firstly, fashion experts found numerous social media influencers and created a specific ``fashion-oriented`` panel. With the same methodology than for the main panel, a normalized time series representing each fashion trend on this specific population is created. we named \textit{fashion-forwards} this first weak signal. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}. 
let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, we compute the following input for our hybrid model: 
for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.

Secondly, depending of the number of followers, the general panel of users is divided in three: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers. Repeating our methodology on each sub-panel, three normalized time series for each time series is created.  Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal. let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,

@@

We split the dataset into three blocks, train, eval and test sets. We use the 3 first years as train set, keep the 4th year for the evaluation set and hide the last year for the test set. We trained the hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
Using the two first year of the train set, we fit a first per-time-series parametric model for each time series. With the resulting collection of local models, we compute a first forecast of the third year for each sequence. Using these forecasts, we preprocess  time series and finally compute the RNN inputs. In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year. We preprocess time series and evaluate how the error-corrector RNN is able to improve the first collection of predictions of the fourth year. The same process is repeated for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.

@@

For the first parametric per-time-series models, we used existing Python or R libraries to estimate the different parameters $\statparam^n$. %During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training. In our framework,
%$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
We propose two versions of HERMES depending of the choice of local parametric models. The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one uses as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset. For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension. We use a classical Adam optimizer with a learning rate set at 0.001 or 0.005, a batch size equal to 64 and the following loss function:

@@

Previous parameters are all set with a grid search and our code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.

@@

As benchmarks, we chose several well-known statistical methods and deep learning approaches. Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , we compute for each time series a prediction with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}. The forecast of the \textit{snaive} method is only the repetition of the last same past period. \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component. \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model. \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization. The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters. A complete description and references for these models can be found in \citep{hyndman2020package}. As a deep learning approach, we considered a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52.

We propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}. The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model. For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}. 
%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
Moreover, we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.

To compare the different methods, we use the Mean Absolute Scaled Error (MASE). As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, we choose this metric to compute a fair error measure, totally independante of the scale of the sequence. The MASE metric is defined as follow:

@@

Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, we also compare the different methods on a classification task and especially difference between method using weak signals or not. In a given year, we define an increasing trend as a trend that does more than 5\% of growth in terms of Year and Year. In the same way, we define a decreasing trend as a trend that declines by 5\% or more. We classify other trends as flat trends. With this threshold, our dataset is almost balanced on the test set : we have 3087 increasing trends, 3342 decreasing trends and 3571 flat trends. On the test set, we compute for each method the accuracy defined as follow :

@@

For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation. For the statistical models, we can see a large domination of TBATS. It is one of the main motivations why we use this model on our best HERMES candidate as the predictor model. %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825. \textcolor{red}{OWA dans le tableau ?}

@@

Models using our weak signals perform similarly as without-weak-signals models for the MASE. In Figure~\ref{fig:introexamples}. Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.

@@

 The impact of our weak signal is revealed with our classification results. Classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa. Our \textit{hermes-tbats} divides  by 3 tis error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions. However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of errors.

When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.

>>>>

Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals. This new architecture is decomposed  into two parts: local predictors and a global corrector.  First, a per-time-series parametric statistical model is trained on all sequences. Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models. By adding external weak signals in the proposed framework, the real potential of the hybrid approach is revealed: a global neural network, able to leverage large amount of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of any parametric models.
%Our new hybrid framework is divided in two parts. As a first step, we compute a per-time-series forecast for each trend using any kind of parametric models. Then, gathering information of the first prediction and external variables, a global error corrector neural network is trained to correct weaknesses of the first forecast.

@@

The paper is organized as follow. Section~\ref{sec:hybrid} describes the hybrid framework. Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes the HERMES results and comparisons with several benchmarks. Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector. Per-time-series parametric models are used to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, a recurrent neural networks is trained to correct the predictions provided by the first collection of per-time-series models.

@@

During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor result and instability. In this paper, a more general framework able to deal with any kind of per-time-series models is provided. In Section~\ref{sec:exp}, two versions of our framework are proposed. The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction. %The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.

In the specific application of fashion trends prediction, two main forms of standard weaknesses was detected and defined for an univariate parametric forecast as defined above. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal are not mainly know. It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals. First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}

@@

The second part of the model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. First, without a well-design input, the RNN will not capable of understanding the initial collection of forecasts and predict their future errors. Second, as no assumption about the scale of our time series was made, inputs require a careful normalization before feeding them to the RNN.
Consider the following pre-processing. 
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$, 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad\mbox{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
$$

@@

Using well-fitted time-series-specific parametric models, the new hybrid network corrects the first form of weakness and achieves striking accuracy on the provided fashion dataset, see Table~\ref{tab:metricresults}. Then, to correct the second form of weakness, in addition to the $N$ target time series, $K \times N$ external sequences indexed from $0$ to $T$ are considered. For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$. Let  $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ be all the values of the weak signals linked to the $n$-th sequence. In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the sequence. Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, a new input for the RNN is defined:   
$$
\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
$$
Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ the final prediction becomes:
%$$
%\tspred^n_{T+i|T} 
%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
%$$
\begin{equation}
\label{eq:withws:full:model}
\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
\end{equation}

@@

\subsection{Translate fashion to data}
\label{sec:dataset:a}
A collection of vision neural networks have been designed and trained  at detecting clothes details on pictures: cloth type (pants, shoes, top etc...), form, size,color,texture etc... Then, with the knowledge of a team of fashion experts, these clothes details was aggregated in order to define a fashion trend: a meaningfully combination of items that represents an existing trend in the fashion sphere. To represent finely the society behaviours based on social media, a group of thousands of random users, called a panel, have been created on several geolocalisations. Analysing every day images shared on social networks by these panels with the previous computer vision system, we are finally able to translate the history of thousand of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.

\subsection{Fashion dataset}
\label{sec:dataset:b}

@@

In addition to this paper, a fashion dataset is proposed. It contains an sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. Some sequences show interesting behaviours with sudden changes. They are called them emerging or declining trends depending on the change in direction. A central point of this work is to accurately detect and forecast these trends.

@@

In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. In this way, several weak signals for each sequence are added to the proposed large dataset.

Firstly, numerous social media influencers was selectioned by hand and aggregatim them, a specific ``fashion-oriented`` panel was created. With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. we named \textit{fashion-forwards} this first weak signal. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}. 
let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model: 
for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.

Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers. Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.  Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal. let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Based on them, two inputs for our hybrid model are computed  : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,

@@

For the needs of the training process, the dataset is temporally splitted into three blocks, train, eval and test sets. the 3 first years are used as the train set, the 4th year is kept for the evaluation set and the last year is hid for the test set. the hyrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
Using the two first year of the train set, a first per-time-series parametric model for each time series is fitted. With the resulting collection of local models, a forecast of the third year is computed for each sequence. Using these forecasts, RNN inputs are finally computed. for the eval set, per-time-series predictors are fitted a second time using the three first years and a forecasts of the fourth year are computed. The eval set is used during the training to control the learning of the RNN model and prevent overfitting. the per-time-series predictors are fitted a last time for the test set using the four first years. The final accuracy measures of all our models are computes on this test set. As an illustraation, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.

@@

For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$. %During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training. In our framework,
%$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. 
depending of the choice of local parametric models, two versions of HERMES are proposed. The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one uses as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on the fashion dataset. The neural network part architecture is summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension. A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follow :

@@

The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix). the code is developed in Python using the Tensorflow library. It allows the use of a GPU to speed up the trainig process.

@@

As benchmarks, Several well-known statistical methods and deep learning approaches was selected. Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats} , for each time series, a prediction was computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}. The forecast of the \textit{snaive} method is only the repetition of the last same past period. \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component. \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model. \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} is a powerful statistical model using a trigonometrical seasonality modelization. The last one \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters. A complete description and references for these models can be found in \citep{hyndman2020package}. As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
Two versions of HERMES are proposed. They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}. The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model. For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}. 
%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
Moreover, two versions with the inclusion of the weak signals (ws) are proposed . They are referred as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.

To compare the different methods, we use the Mean Absolute Scaled Error (MASE). As our time series have complete different scale, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, totally independante of the scale of the sequence. The MASE metric is defined as follow:

@@

Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, the different methods are also compared on a classification task and especially difference between methods using weak signals or not. In a given year, an increasing trend is defined as a trend that does more than 5\% of growth in terms of Year and Year. In the same way, a decreasing trend is defined as a trend that declines by 5\% or more. Other trends are classified as flat trends. With this threshold, the proposed fashion dataset is almost balanced on the test set : There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends. On the test set, for each method, the accuracy defined as follow is computed:

@@

For the two metrics and for each model, we compute the average on all our sequences \numberts~  on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, 10 models are trained  with different seeds. The average and the standard deviation of their results are computed and displayed. For the statistical models, TBATS largely dominate in term of MASE. It is one of the main motivations why this model is used on our best HERMES candidate as the predictor model. %However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825. \textcolor{red}{OWA dans le tableau ?}

@@

Models using our weak signals perform similarly as without-weak-signals models for the MASE. In Figure~\ref{fig:introexamples}. Interestingly, weak signals sinificantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknessess that can be corrected.

@@

The impact of the weak signals are revealed with our classification results. Classification results between the \textit{tbats} model and the hybrid method \textit{hermes-tbats} are given in Table~\ref{tab:tbatsclass}, we note an impresive decrease of impactful errors: forecast an increase instead of a decrease and vice versa. Our \textit{hermes-tbats} divides by 3 the error rate in comparison to \textit{tbats} with only a slightly decrease of the number of correct increase/decrease predictions. However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of errors.

%When we look at the result of \textit{lstm-ws} and \textit{lstm} displayed in Table~\ref{tab:lstmclass}, we can also note a rise of the number of correct predictions but with an important increase of the number of classification errors.
